Bullet Groups as a test of $\Lambda$CDM

### 2014-02-27 paper/ms.tex
new structure

\documentclass[12pt,preprint]{aastex}
% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}

\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{epsfig}  
\usepackage{float}
%\bibliographystyle{apj}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

@@

\title{Bullet Groups in the Bolshoi Cosmological Simulation}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$ and T. Vergudo$^3$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne, Besan\c{c}on, France\\
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264, M\'erida 5101-A, Venezuela}

\begin{abstract}

We estimate the expected distribution of displacements between the host halo of dark matter and the 
substructure of dark matter most massive of the host, using a halo catalog from the Bolshoi simulation detected 
with the Bound Density Maximun (BDM) algorithm. We found that the probability of finding a system similar to the Bullet
Group with displacements of $\sim$400 kpch$^{-1}$ is between 40\% for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard 
model predicts this scenario and is consistent with recently observations of the object SL2S J08544-0121 that is 
a gravitational lens found in the SL2S and located at z$=0.35$.

\end{abstract}

@@

This paper is organized as the follows: In Section
\ref{simulation} we present the simulations.

\section{Simulation}
\label{simulation}

@@

\section{Cumulative Probability Distributions}
\label{cumulative distribution}

We selected four snapshot of the simulation for four different redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the 
distribution of redshift in the Figure 1 by \citet{verdugo}, and 
for each sample in redshift we selected the host halo with circular velocities greater than 300 kms$^{-1}$ and was split in two 
principal groups: The first group correspond to host halo with circular velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$
with mass in the range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range of mass of the
Bullet Groups, and second group correspond to host halo with circular velocities greater than 
700 kms$^{-1}$ with mass $\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet Clusters, in 
the Table \ref{table1} is shown the two groups selected in this work. For each group, we 
classified the corresponding substructures most massive and associated with the corresponding 
host halo. The configuration of this system is shown in 
Figure \ref{configuration}, where you can distinguish the host halo and substructure for a particular configuration in z$=0$. In 
this work, we estimate the expected distribution of displacements ($d_{real,(X,Y)}$) in the projection 2-D that can estimate by 
observations, these displacements correspond to the separation between the minimal potential of the host halo and the 
minimal potential of the substructure, both are dark matter distributions.\\

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs $d_{2d,(X,Y)}$ for different redshifts. The 
horizontal dashed line correpond to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the red star simbol correspond
to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S SJ08544-0121 in \citet{2013A&A...552A..80M}. The 
four top panels are the sample with circular velocities $>700$ kms$^{-1}$ and the four down panels are the sample with 
circular velocities between 300 km s$^{-1}$ to 700 kms$^{-1}$.}
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements for the projection (X,Y). {\bf Left panel:} Sample with $\nu_{max}>700$ kms$^{-1}$ 
for different redshifts. The vertical dashed line, correspond to the separation between dark matter to dark matter estimate
in this work as the double of separation between the collisional gas and dark matter of 124$\pm$20 kpc reported
by \citet{gastaldello} for the group SL2S J08544-0121. 
{\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $ kms$^{-1}$ for different redshifts.} 
\label{displacements}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

\section{Summary}
\label{summary}

\section{Conclusions}
\label{conclusions}

@@

\begin{thebibliography}{29}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Klypin} {et~al.}(2011)}]{2011ApJ...740..102K}
{Klypin}, A.~A. and {Trujillo-Gomez}, S. and {Primack}, J.} 2011, \apj, 102

\bibitem[{{Verdugo} {et~al.}(2014)}]{verdugo}
{{Vedugo}, T., {Motta}, V., {Foex}, G., {Forero-Romero}, J. E., {Mu\~noz}, R. P., {Pello}, R., 
{Limousin}, M., {Gavazzi}, R., {More}, A., {Cabanac}, R., {Soucail}, G., {Blakeslee}, J. P., 
{Mej\'ia}, A., {Magris}, G. and {Fern\'andez-Trincado}, J. G.} 2014, \apj, in preparation

\bibitem[{{Gastaldello} {et~al.}(2014)}]{gastaldello}
{{Gastaldello}}, F., et al. 2014, \mnras, in preparation

\bibitem[{{Mu\~noz} {et~al.}(2013)}]{2013A&A...552A..80M}
{{Mu{\~n}oz}, R.~P. and {Motta}, V. and {Verdugo}, T. and {Garrido}, F. and 
{Limousin}, M. and {Padilla}, N. and {Fo{\"e}x}, G. and {Cabanac}, R. and 
{Gavazzi}, R. and {Barrientos}, L.~F. and {Richard}, J.} 2013, \aap, A80

%%%%%%%%%%%%%%%%%%%%%%

%\bibitem[{{Tormen}(1997)}]{1997MNRAS.290..411T}
%{Tormen}, G. 1997, \mnras, 290, 411

%\bibitem[{{Tormen} {et~al.}(2004){Tormen}, {Moscardini}, \&
%  {Yoshida}}]{2004MNRAS.350.1397T}
%{Tormen}, G., {Moscardini}, L., \& {Yoshida}, N. 2004, \mnras, 350, 1397

%\bibitem[{{Vitvitska} {et~al.}(2002){Vitvitska}, {Klypin}, {Kravtsov},
%  {Wechsler}, {Primack}, \& {Bullock}}]{2002ApJ...581..799V}
%{Vitvitska}, M., {Klypin}, A.~A., {Kravtsov}, A.~V., {Wechsler}, R.~H.,
%  {Primack}, J.~R., \& {Bullock}, J.~S. 2002, \apj, 581, 799

%\bibitem[{{Yepes} {et~al.}(2007){Yepes}, {Sevilla}, {Gottl{\"o}ber}, \&
%  {Silk}}]{2007ApJ...666L..61Y}
%{Yepes}, G., {Sevilla}, R., {Gottl{\"o}ber}, S., \& {Silk}, J. 2007, \apjl,
%  666, L61

\end{thebibliography}

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{epsfig}  
\usepackage{float}
\bibliographystyle{apj}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

@@

\title{Bullet Groups as a test of $\Lambda$CDM}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$
  and T. Verdugo$^3$} 
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
  Besan\c{c}on, France\\ 
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
  M\'erida 5101-A, Venezuela}

\begin{abstract}
We estimate the expected distribution of displacements between the two
dominand dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

@@

This paper is organized as the follows. In Section
\ref{sec:simulation} we present the simulation and the halo catalogs
used in this work. We continue in Section \ref{sec:setup} with the
geometry of the problem at hand and the measurements setup. Next in
Section \ref{sec:results} we present our results to finish with a
discussion and conclusion in Sections \ref{sec:discussion} and
\ref{sec:conclusions}.

\section{Simulation and halo catalogs}
\label{sec:simulation}

@@

\section{Bullet Geometry and Measurement Setup}
\label{sec:setup}

\section{Results}
\label{sec:results}

\subsection{Cumulative Probability Distributions}
\label{cumulative_distribution}

We selected four snapshot of the simulation for four different
redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the
distribution of redshift in the Figure 1 by \citet{verdugo}, and  for
each sample in redshift we selected the host halo with circular
velocities greater than 300 kms$^{-1}$ and was split in two  principal
groups: The first group correspond to host halo with circular
velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$ with mass in the
range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range
of mass of the Bullet Groups, and second group correspond to host halo
with circular velocities greater than 700 kms$^{-1}$ with mass
$\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet
Clusters, in  the Table \ref{table1} is shown the two groups selected
in this work. For each group, we  classified the corresponding
substructures most massive and associated with the corresponding host
halo. The configuration of this system is shown in  Figure
\ref{configuration}, where you  an distinguish the host halo and
substructure for a particular configuration in z$=0$. In  this work,
we estimate the expected distribution of displacements
($d_{real,(X,Y)}$) in the projection 2-D that can estimate by
observations, these displacements correspond to the separation between
the minimal potential of the host halo and the  minimal potential of
the substructure, both are dark matter distributions.

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

@@

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

@@

\bibliographystyle{apj}
\bibliography{references}
